Title

### 2023-05-22 main.tex
SIMONE, WE WENT OVER THIS. EXPANDTAB.

% }}}
\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
\tbnote{Lo cambié}
\cpnote{El texto esta bien, pero creo qeu la distribucino de subsecciones esta chistosna y 
los titulo tambien. Platicar con Tomas a ver a que llegamos. }

% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} \tbnote{Ya} we introduce the
concept of quantum channels, focusing on a specific type called Pauli channels.
Furthermore, we define Pauli dynamical maps, which
are curves of Pauli channels parametrized by a variable.
% }}}
%\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

% \cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
% \cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
% lo qeu se quiere decir en la seccion es otra cosa.}

@@

\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
\tbnote{Perfecto, gracias!}
% }}}
\subsection{Pauli Channels} 
\label{subsec: Pauli Channels} % {{{

@@

\cpnote{Acá voy}

% \cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso
% a ver como reorganizar las secciones (creo que el flujo si va bien hasta
% ahora)} \tbnote{Va. Me pareció ponerle su propia subsección a la parte anterior
% porque creo que esto y lo anterior sí debe ir separado, así que mejor dos
% subsecciones.}

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the state 
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}})
\label{eq:angle2} \\
\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
on them.
%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this {\color{red}
Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}

We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels \cpnote{Revisa esta 
frase a ver si te parece} 
\tbnote{Sí, perfecto}.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
definido matemáticamente} \tbnote{Qué tal así:} {\color{orange}, defined by 
\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.}

Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

@@

% }}}
% }}}

\newpage
\section{One Parameter Circuits} % {{{
\label{sec: 1PR Circuits}
\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
\cpnote{No se sabe aun que son 1PR circuits. Poner completo} \tbnote{Ya.}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/curvas.png}
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in the tetrahedron
represent Pauli dynamical maps that can be implemented with 1PR circuits.
In particular, the depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange). }
\label{fig:curves}
\end{figure}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/curvas-azar.png}
\caption{{\bf Random Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in the tetrahedron
represent Pauli dynamical maps that can be implemented with 1PR circuits
that were selected at random using the procedure detailed before.}
\label{fig:curves-random}
\end{figure}

>>>>

% }}}
\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
% Intro  {{{
% \textbf{Lista de puntos:}
% \begin{itemize}
% \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
% \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
% \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
% \end{itemize}

In this section  we introduce the concept of quantum channels, focusing on a
specific type called Pauli channels.  Furthermore, we define Pauli dynamical
maps, which are curves of Pauli channels parametrized by a variable.
% }}}
\subsection{Quantum Channels} \label{subsec: Quantum Channels} % {{{

@@

% }}}
\subsection{Pauli Channels}  \label{subsec: Pauli Channels} % {{{

@@

For the particular case of a Pauli channel on one qubit, the circuit that
simulates it can be constructed as in \fref{fig: circuit-pauli-1},
which is a special case of \fref{fig: circuit-pauli}
but with all details  explicitly shown.
In said figure, the state 
$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
is created on the ancilla qubits with the help of three rotations of angles:
\begin{subequations}
\begin{eqnarray}
\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle1} \\ 
\theta_1 &= &2 \arccos(\sqrt{k_{00} +
k_{01}})
\label{eq:angle2} \\
\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
\label{eq:angle3}
\end{eqnarray}
\label{eq:angle}
\end{subequations}
\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
que quizá estén mas bonitas.}

\begin{figure} % {{{
\centering
\includegraphics{images/circuito_unqubit.pdf}
\caption{
% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
ancilla qubits and we use three rotations
of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}}
|00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
|10\rangle + \sqrt{k_{11}}|11\rangle$
on them.
\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
a la ecuación.}
%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
}
\label{fig: circuit-pauli-1} 
\end{figure} % }}}

Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
one-qubit Pauli channels and simulated them using the ibmq-lima quantum
computer\cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
la frase.}.  For each of these channels, we used quantum process
tomography~\cite{Qiskit, Chuang:1996} to obtain the 
operator $\xi_I$ corresponding to the implementation of the
circuit.  Then, we compared this operator with the ideal 
channel $\xi_T$  we
wanted to implement.

\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }
We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
with the probability that one can distinguish two channels.
% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
% which gives us a method of discriminating \cpnote{no solo discrimina... todas
% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
% no conecta bien con lo que sigue}.
In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
with probability $1/2$ each,
and tries to guess which channel they received
by applying it to a state $\rho$ and measuring the result.
Then, the maximal probability of success (out of all possible states $\rho$) that
the agent guesses correctly is~\cite{Benenti}:
\begin{equation}
\label{eq: probability-success}
p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
\end{equation}
where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by 
\begin{align*}
||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
\end{align*}
with $I$ the identity map,
$|| \cdot ||_1$ the trace norm and the maximization
done over all density matrices $\rho$.
\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
calculas. }

Notice that if the channels are the same, then $p_{\succ}=1/2$. 
This is expected because in this situation the agent
has no way of distinguishing the channels and has no choice but to completely
guess, which results in a probability of success of $1/2$.
On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
distinguishable.
\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
% \cpnote{hummm ejemplo al menos para nosotros.} 
% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
% (para $i\neq j$), se cumple esto.
% También quería ejemplos no unitarios, pero no encontré.}

@@

% }}}
% }}}
\section{One Parameter Circuits} % {{{
\label{sec: 1PR Circuits}
\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
\cpnote{No se sabe aun que son 1PR circuits. Poner completo} \tbnote{Ya.}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/curvas.png}
\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in the tetrahedron
represent Pauli dynamical maps that can be implemented with 1PR circuits.
In particular, the depolarizing (purple), bit flip (blue),
phase flip (green), bit-phase flip (red)
and parabolic (orange). }
\label{fig:curves}
\end{figure} % }}}

@@

\begin{figure} % {{{
\centering
\includegraphics{images/curvas-azar.png}
\caption{{\bf Random Pauli dynamical maps that can be implemented with a 1PR circuit.}
The curves painted in the tetrahedron
represent Pauli dynamical maps that can be implemented with 1PR circuits
that were selected at random using the procedure detailed before.}
\label{fig:curves-random}
\end{figure} % }}}
